---
title: "TidyTuesday Visualizations"
format: 
  html:
    toc: false
    page-layout: full
---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(readr)

# Read the CSV directly from your TidyTuesday GitHub repo
csv_url <- "https://raw.githubusercontent.com/louiewee/TidyTuesday/refs/heads/main/data/tidytuesday_plots.csv"

# Try to read the CSV
tryCatch({
  plots_data <- read_csv(csv_url, show_col_types = FALSE)
  cat("✅ Successfully loaded", nrow(plots_data), "plots from TidyTuesday repo\n")
}, error = function(e) {
  plots_data <<- data.frame(
    image_path = character(0),
    packages = character(0)
  )
  cat("⚠️ Could not load CSV from TidyTuesday repo.\n")
})
```

<style>
.gallery {
  display: grid;
  grid-template-columns: repeat(auto-fill, minmax(300px, 1fr));
  gap: 20px;
  padding: 20px 0;
}

.gallery-item {
  cursor: pointer;
  transition: transform 0.3s ease;
  border-radius: 8px;
  overflow: hidden;
  box-shadow: 0 2px 8px rgba(0,0,0,0.1);
}

.gallery-item:hover {
  transform: scale(1.05);
  box-shadow: 0 4px 16px rgba(0,0,0,0.2);
}

.gallery-item img {
  width: 100%;
  height: 250px;
  object-fit: cover;
  display: block;
}

/* Modal styles */
.modal {
  display: none;
  position: fixed;
  z-index: 1000;
  left: 0;
  top: 0;
  width: 100%;
  height: 100%;
  background-color: rgba(0,0,0,0.9);
  cursor: pointer;
}

.modal-content {
  position: absolute;
  top: 50%;
  left: 50%;
  transform: translate(-50%, -50%);
  max-width: 90%;
  max-height: 90%;
  cursor: default;
}

.modal-content img {
  width: 100%;
  height: auto;
  border-radius: 8px;
}

.close {
  position: absolute;
  top: 20px;
  right: 35px;
  color: #f1f1f1;
  font-size: 40px;
  font-weight: bold;
  cursor: pointer;
}

.close:hover {
  color: #ccc;
}
</style>

## Portfolio Projects

[TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/main/README.md) is a weekly social data project organized by the [Data Science Learning Community](https://dslc.io/).

Complete code can be accessed [here](https://github.com/louiewee/TidyTuesday).

```{r filters, echo=FALSE, results='asis', eval=nrow(plots_data) > 0}
if (nrow(plots_data) > 0 && "packages" %in% colnames(plots_data)) {
  
  # Get unique packages without pipes
  packages_list <- strsplit(plots_data$packages, ",")
  all_packages_raw <- unlist(packages_list)
  all_packages_trimmed <- trimws(all_packages_raw)
  all_packages_unique <- unique(all_packages_trimmed)
  all_packages <- sort(all_packages_unique)
  
  # Remove empty packages
  all_packages <- all_packages[all_packages != "" & !is.na(all_packages)]
  
  if (length(all_packages) > 0) {
    cat('<div class="filter-section">\n')
    cat('<button class="filter-btn active" data-filter="all">All</button>\n')
    
    for (pkg in all_packages) {
      cat('<button class="filter-btn" data-filter="', pkg, '">', pkg, '</button>\n')
    }
    
    cat('</div>\n')
  }
}
```

```{r gallery, echo=FALSE, results='asis'}
if (nrow(plots_data) > 0) {
  
  cat('<div class="gallery">\n')
  
  for (i in 1:nrow(plots_data)) {
    image_path <- as.character(plots_data$image_path[i])
    
    # Convert to GitHub raw URL
    image_url <- ifelse(
      startsWith(image_path, "http"),
      image_path,
      paste0("https://raw.githubusercontent.com/louiewee/TidyTuesday/refs/heads/main/", image_path)
    )
    
    # Get packages for this visualization
    packages_raw <- ""
    if ("packages" %in% colnames(plots_data)) {
      packages_raw <- as.character(plots_data$packages[i])
      if (is.na(packages_raw)) packages_raw <- ""
    }
    
    # Create space-separated package list for data attribute
    packages <- trimws(strsplit(packages_raw, ",")[[1]])
    packages <- packages[packages != "" & !is.na(packages)]
    package_classes <- paste(packages, collapse = " ")
    
    cat('<div class="gallery-item" data-packages="', package_classes, '">\n')
    cat('  <a href="', image_url, '" target="_blank">\n')
    cat('    <img src="', image_url, '" alt="TidyTuesday Visualization" loading="lazy">\n')
    cat('  </a>\n')
    cat('</div>\n')
  }
  
  cat('</div>\n')
  
} else {
  cat('<div class="alert">')
  cat('<p>No visualizations found. Check out my TidyTuesday repository: <a href="https://github.com/louiewee/TidyTuesday">github.com/louiewee/TidyTuesday</a></p>')
  cat('</div>')
}
```

<!-- Modal removed - using new tab instead -->

<script>
// Wait for the page to load
document.addEventListener('DOMContentLoaded', function() {
  
  // Add click listeners to filter buttons
  const filterButtons = document.querySelectorAll('.filter-btn');
  const galleryItems = document.querySelectorAll('.gallery-item');
  
  filterButtons.forEach(function(button) {
    button.addEventListener('click', function() {
      const filter = this.getAttribute('data-filter');
      
      // Update button states
      filterButtons.forEach(btn => btn.classList.remove('active'));
      this.classList.add('active');
      
      // Filter gallery items
      galleryItems.forEach(function(item) {
        const itemPackages = item.getAttribute('data-packages') || '';
        
        if (filter === 'all') {
          item.style.display = 'block';
        } else {
          if (itemPackages.includes(filter)) {
            item.style.display = 'block';
          } else {
            item.style.display = 'none';
          }
        }
      });
    });
  });
});
</script>